Blocking-resistant communication\\through domain fronting

### 2014-11-23 docs/meek.tex
edits

@@

Microsoft Azure~\cite{azure}
is a cloud computing platform that features a CDN.
Similarly to CloudFront, users get automatically generated subdomains
of \urll{vo.msecnd.net},
all of which can front for each other.
There are other front domain names, like \urll{ajax.aspnetcdn.com},
that may offer high collateral damage.

@@

Development on \meek\ as a Tor pluggable transport~\cite{pt} began in January~2014.
Most users who use Tor use it with Tor Browser~\cite{torbrowser},
a customized version of Firefox that is
preconfigured to use a built-in Tor client.
% and patched to defend against application-layer privacy and anonymity threats
% like tracking cookies and web browser fingerprinting.
Tor Browser has an easy interface for selecting pluggable transports.
We made a series of experimental releases of Tor Browser featuring \meek,
releasing the first one on February~18.
[Some details of deployment are omitted for anonymous submission.]
% ANON
% On April~18 we made the first release featuring the browser camouflage
% that is the subject of Section~\ref{sec:browserextension}.
% We announced our releases on Tor development mailing lists,
% whence they were picked up by Tor Weekly News on the Tor blog.
% Our code was merged by the Tor Browser maintainers
% in June and is scheduled for an alpha release,
% still pending as of this writing.

\begin{figure}
\includegraphics[width=\linewidth]{clients-meek}
\caption{
Concurrent users of the \meek\ pluggable transport for Tor.
}
\label{fig:clients-tor}
\end{figure}

@@

Figure~\ref{fig:clients-tor} shows the average number of concurrent users of \meek\ with Tor
since close to the beginning of development.
A measurement of 500, for example, means that there were on average 500
users of the system at any given time during the day.
The measurements come from the Tor Metrics Portal~\cite{metrics-meek},
which aggregates statistics reported by Tor relays.
The number of users is estimated by counting the number
of Tor directory requests made by clients~\cite{counting-daily-bridge-users}.
% The drop to zero on May~8 coincides with the reinstallation of the Tor bridge used by \meek.

@@

Our experimental Tor Browser releases have all been based on Google with App Engine.
Support for CloudFront was not realized until late July.
We are running the backends on paid accounts of these services for use by the public.
The cost for bandwidth on App Engine is \$0.12 per gigabyte,
with one gigabyte free each day.
The total App Engine bill so far has been \$2.07,
with most days' usage being below the billable threshold.
There has not yet been enough use of CloudFront to cost anything.

A longer-term goal is to find a way to fund continued operation
if \meek\ becomes popular.
Although some of the systems listed in Section~\ref{sec:survey}
are inexpensive enough that some users could upload their own fronting backend,
thereby diffusing costs,
we believe that an organization operating a backend for the use of the public
has compelling usability advantages.
With client software configured to use the public backend by default,
there is nothing for the user to upload and no out-of-band communication is needed before getting
started---when everything works it offers circumvention without configuration.

>>>>

Microsoft Azure~\cite{azure}
is a cloud computing platform that features a CDN.
Similarly to CloudFront, users get automatically generated subdomains
of \urll{vo.msecnd.net},
all of which can front for each other.
The CDN works only for Azure domains, however,
so as with App Engine, it is necessary to run a trivial reflector app
that merely forwards requests out of Azure toward an external proxy.
There are other front domain names, like \urll{ajax.aspnetcdn.com},
that may offer high collateral damage.

@@

@@

Development on \meek\ as a Tor pluggable transport~\cite{pt} began in January~2014.
Our target for deployment is Tor Browser~\cite{torbrowser},
a customized version of Firefox that is
preconfigured to use a built-in Tor client.
% and patched to defend against application-layer privacy and anonymity threats
% like tracking cookies and web browser fingerprinting.
Tor Browser has an easy interface for selecting pluggable transports.
% ANON
% [Some details of deployment are omitted for anonymous submission.]
% We made a series of experimental releases of Tor Browser featuring \meek,
% releasing the first one on February~18.
% On April~18 we made the first release featuring the browser camouflage
% that is the subject of Section~\ref{sec:browserextension}.
% We announced our releases on Tor development mailing lists,
% whence they were picked up by Tor Weekly News on the Tor blog.
% Our code was merged by the Tor Browser maintainers
% in June and is scheduled for an alpha release,
% still pending as of this writing.

We have so far deployed on three backends:
Google App Engine,
Amazon CloudFront,
and Microsoft Azure.
Figure~\ref{fig:clients-tor} shows the daily average number of concurrent users of \meek.
(A measurement of 500, for example, means that there were on average 500
users of the system at any given time during the day.)
The App Engine backend was established in February;
CloudFront in July;
and Azure in October.
Also in Figure~\ref{fig:clients-tor} is a table of monthly costs for each web service.
The pricing for cloud services is complicated,
depending not only on bandwidth but also on geographical region and other factors.
For example CloudFront charges per request as well as per gigabyte,
and about 54\% of the CloudFront bill for October was for requests.
App Engine charges extra when it has to run multiple instances
of an app's code to cope with load;
about 15\% of October's App Engine bill was for such ``instance hours.''
% These and other cost details are summarized in a mailing list post~\cite{meek-costs-201410}.
The App Engine and CloudFront backends are running on accounts
that provide a limited amount of free bandwidth,
but current use greatly exceeds the free thresholds.
Azure service is being donated and so has not yet cost anything.
The total cost so far has been \$187.13,
but this number is expected to more than double in November and continue to increase.

\begin{figure}
\centering
\includegraphics[width=\linewidth]{clients-meek}
\begin{tabular}{l r r r}
       &App Engine &CloudFront&  Azure \\
\hline
Jan--Jul &  \$2.72 &   \$0.00 & \$0.00 \\
Aug      &  \$1.56 &   \$3.10 & \$0.00 \\
Sep      &  \$4.02 &   \$4.59 & \$0.00 \\
Oct      & \$40.85 & \$130.29 & \$0.00 \\
\hline
total    & \$49.15 & \$137.98 & \$0.00 \\
\end{tabular}
\caption{
Concurrent users of the \meek\ pluggable transport
and month-by-month operational costs.
The total cost to date is \$187.13.
% ANON
% The large increase of users on October~15 coincides with
% the release of Tor Browser~4.0,
% the first release to make meek easily available.
Azure CDN service is currently being donated as part of a research grant.
The user estimates come from the Tor Metrics Portal~\cite{metrics-meek,counting-daily-bridge-users}.
}
\label{fig:clients-tor}
\end{figure}

@@

%  &\$49.15 & \$137.98 & \$0.00 & \$187.13 &  \\

% which aggregates statistics reported by Tor relays.
% The number of users is estimated by counting the number
% of Tor directory requests made by clients~\cite{counting-daily-bridge-users}.

@@

As users increase, it becomes more pressing
to find a way to sustain continued operation.
Although some of the systems listed in Section~\ref{sec:survey}
are inexpensive enough that some users could upload their own fronting backend
and bear their own costs,
we believe that there are compelling usability advantages
to operating a centralized backends for the use of the public.
Client software can ship with preconfigured domain names.
There is nothing for the user to upload and no out-of-band bootstrapping communication is needed.
